---
title: "Analyzing International Soccer Games 1872-2022"
author: "Shira Zur, Deeana Nasrulai, Nathan Beh"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Data:

The visualizations below focus on various relationships we observed and analyzed in our soccer results data. The first visualization looks at the total number of goals scored by each country over time, ranging from 1872 to present day. The second visualization focuses on the Home Game Advantage, a theory that states that a team playing at their home stadium are more likely to win, rather than when they play away at the opposing team's stadium. The visualization compares the home win ratio versus the away win ratio over each decade. Lastly, the third visualization compares the team performance of two teams -- England and Scotland. The line graph visualization shows the total number of goals scored by the two teams over time. We hope our visualizations help improve the analysis of soccer teams and soccer games and show how versatile soccer analysis can be.  


## World Density Map

This World Density Map shows the total number of goals scored by each country from 1872-2022.

```{r, echo = FALSE, message = FALSE, results = 'hide'}
source('../source/Deeana_source_file.R')
plot(worldMap1)
```

This goal density visualization allows us to see a big picture overview of National team performances from the start of data collection. This could provide analysis that could help national teams/players/supporters be informed on the status of their team's success. This also informs us which team has been the most dominant in the history of soccer.

## Home vs. Away Bar Chart

This Home vs. Away Wins Ratio Bar Chart shows the overall home ratio (home wins out of total home games) and away ratio (away wins out of total away games) during every decade.

```{r, echo = FALSE, message = FALSE, results = 'hide'}
source('../source/Shira_source_file.R')
plot(ratio_barplot)
```

This bar chart proves the home game advantage theory -- a theory that states that teams that play a match in their home city are more likely to win than teams that play a match away, at a city they are not from. This bar chart could help team managers and coaches that are worried that the home game advantage may no longer serve them; they can refer to this analysis and see that when they play home, they will be much more likely to win, and therefore need to prepare their teams when they play away.

## Summary Table

This table allows the reader to explore the raw data points we used in order to create the visuals displayed below. Having a table that displays this raw data is important because it allows the reader to not only use or analysis but be able to create their own conclusions because we provided them with as much information as possible and not only our visuals of the manipulated data.

```{r, echo = FALSE, results = 'asis', message = FALSE}
library(dplyr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggmap)
source('../source/table.sourcefile.R')
total_goals_by_team %>%
  kbl() %>%
  kable_styling() %>% 
  scroll_box(
  height = "500px",
  width = "500px",
  box_css = "border: 1px solid #ddd; padding: 5px; ",
  extra_css = NULL,
  fixed_thead = TRUE
)
```
